Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-18 manuscript/manuscript.Rmd

In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
procedure.

@@

```{r variables, results='asis', message=FALSE, echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~Variable, ~Type,
  "Building insurance coverage", "Numeric",
  "Community Rating System Discount", "Numeric",
  "Basement enclosure type", "Categorical",
  "Occupancy Type", "Categorical",
  "Number of floors in the insured building", "Categorical (binned in original dataset)",
  "Flood zone", "Categorical (high cardinality)",
  "Primary residence", "Categorical (binary indicator)"
)
knitr::kable(
  variables,
  caption = "Predicator variables.",
  booktabs = TRUE,
  table.env = "table",
  escape = FALSE,
  linesep = ""
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

@@

(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance
evaluation only we use all data in CV splits?)

## Models

@@

## Training and Inference

(TODO)

>>>>

In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then develop 
GLMs and neural networks utilizing embeddings for this problem, and inspect the trained parameters. Finally, we
provide details of model optimization, inference, and performance.

@@

```{r variables, results='asis', message=FALSE, echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~Variable, ~Type,
  "Building insurance coverage", "Numeric",
  "Community Rating System Discount", "Numeric",
  "Basement enclosure type", "Categorical",
  "Occupancy Type", "Categorical",
  "Number of floors in the insured building", "Categorical (binned in original dataset)",
  "Flood zone", "Categorical (high cardinality)",
  "Primary residence", "Categorical (binary indicator)"
)
knitr::kable(
  variables,
  caption = "Predictor variables.",
  booktabs = TRUE,
  table.env = "table",
  escape = FALSE,
  linesep = ""
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

@@

For our experiments, we set up a 10-fold cross validation scheme that is applied to each of the models
we introduce. In Sections \ref{models} and \ref{interpretations}, the tables and figures are based on a single fold of 
the cross validation split. In Section \ref{training-inference}, we provide the cross-validated performance
metrics of each of the models.

We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, 
rather than
on fine-tuning models in order to beat or establish a benchmark. To this end, we do not perform systematic
hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable
models utilizing categorical embeddings. However, as we describe the modeling procedure and results, we provide
commentary on recommended practices in practical applications, especially with respect to the neural network models.

## Models {#models}

@@

## Training and Inference {#training-inference}

For the GLMs, Models 1 and 3, we follow the standard optimization procedure using iteratively reweighted least 
squares (IWLS) without regularization. For the neural networks, Models 2 and 4, we utilize the \texttt{Adam}
optimizer [@Kingma2014] with a learning rate of TODO, and train the each network for TODO epochs with a batch
size of TODO.

During inference, or scoring, care must be taken to accommodate the categorical levels that are unseen
during training. While we allow for an extra key in the embedding dictionary (TODO: mention this earlier), the initial
weights are not updated during training, which could lead to nonsensical predictions in the validation or test sets. To
circumvent this issue, before applying the trained model but after the final optimization epoch, we update the weights
for the unseen levels manually. In practice, a common approach is to take an average value 
of some sort of the weights of theother levels. In our case, we take the median (if there are multiple, the lower of
the two), but a mean, mean weighted by frequency of observations, or trimmed mean could be used.

In Table TODO, we exhibit the cross-validated performance metrics of each of the models.
